Acceleration of Derivative Calculations with Application to Radial Basis Function -- Finite-Differences on the Intel MIC Architecture

### 2014-01-17 acm/ieee_paper.tex
minor

Section~\ref{sec:model} presents an
estimation of the instruction intensity of various forms of the
computations. We show that a \ge{sevenfold} \NOTE{sixfold was inconsistent with eighfold in the abstract.} improvement can be
expected when computing the sixteen multiplications simultaneously to
reach a total of about 210~Gflop/s. This performance represents
approximately 10\% of the available flop/s of a Xeon Phi
coprocessor. \ee{Provided the computation is mostly irregular, it is necessary to have an implementation that organizes the data in such a way it can perform a fully efficient Fused Multiply-Add every 10 cycles.} \NOTE{Rewrote, is it more clear?}
\ge{We describe in Section~\ref{sec:impl} the details of the MIC
architecture and how to use specialized load, store, swizzle and
permutation instructions to efficiently bring the data from memory into the vector
registers to be processed. Section~\ref{sec:expe} presents results on 
memory access and computational speed and their relation to choices made in the 
SpMV kernels.}
%experimental results  discussing the relationship between the structure of $A$ and 
%the ; specifcally on the amount of bandwidth that can be achieved
%depending on how the SpMV kernel is written. 
It also provides the actual performance of the various kernels on multiple classes of matrices, 
some generated for purpose of analysis, and some extracted from an application of RBF-FD. 
A performance of 135~Gflop/s in single precision is achieved using RBF-FD differentiation matrices, which is 3.75 imes better than the theoretical peak performance of an SpMV operation. Concluding remarks and perspectives are provided in Section~\ref{sec:ccl}.\looseness=-1

>>>>

Section~\ref{sec:model} presents an
estimation of the instruction intensity of various forms of the
computations. We show that a \ge{sevenfold} \NOTE{sixfold was inconsistent with eighfold in the abstract.} improvement can be
expected when computing the sixteen multiplications simultaneously to
reach a total of about 210~Gflop/s. This performance represents
approximately 10\% of the available flop/s of a Xeon Phi
coprocessor. \ee{Provided the computation is mostly irregular, it is necessary to have an implementation that organizes the data in such a way it can perform a fully efficient Fused Multiply-Add every 10 cycles.} \NOTE{Rewrote, is it more clear?}
\ge{We describe in Section~\ref{sec:impl} the details of the MIC
architecture and how to use specialized load, store, swizzle and
permutation instructions to efficiently bring the data from memory into the vector
registers to be processed. Section~\ref{sec:expe} presents results on 
memory access and computational speed and their relation to choices made in the 
SpMV kernels.}
%experimental results  discussing the relationship between the structure of $A$ and 
%the ; specifcally on the amount of bandwidth that can be achieved
%depending on how the SpMV kernel is written. 
It also provides the actual performance of the various kernels on multiple classes of matrices, 
some generated for purpose of analysis, and some extracted from an application of RBF-FD. 
A performance of 135~Gflop/s in single precision is achieved using RBF-FD differentiation matrices, which is 3.75 times better than the theoretical peak performance of an SpMV operation. Concluding remarks and perspectives are provided in Section~\ref{sec:ccl}.%\looseness=-1
